Extreme heterogeneity of influenza virus infection in single cells

### 2018-02-13 paper/paper.tex
added STR profiling and eLife Github link

\subsection{Cell lines and viruses}
The following cell lines were used in this study: the human lung epithelial carcinoma line A549 (ATCC CCL-185), the MDCK-SIAT1 variant of the Madin Darby canine kidney cell line overexpressing human SIAT1 (Sigma-Aldrich 05071502), and the human embryonic kidney cell line 293T (ATCC CRL-3216). 
The A549 cells were tested as negative for mycoplasma contamination by the Fred Hutch Genomics Core.
All cells were maintained in D10 media (DMEM supplemented with 10\% heat-inactivated fetal bovine serum, 2 mM L-glutamine, 100 U of penicillin/ml, and 100 \si{\micro}g of streptomycin/ml) at 37 \si{\degreeCelsius} at 5 \% CO\textsubscript{2}.

@@

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell}~\citep{russell2018github}.

>>>>

\subsection{Cell lines and viruses}
The following cell lines were used in this study: the human lung epithelial carcinoma line A549 (ATCC CCL-185), the MDCK-SIAT1 variant of the Madin Darby canine kidney cell line overexpressing human SIAT1 (Sigma-Aldrich 05071502), and the human embryonic kidney cell line 293T (ATCC CRL-3216). 
The A549 cells were tested as negative for mycoplasma contamination by the Fred Hutch Genomics Core, and authenticated using the ATCC STR profiling service.
All cells were maintained in D10 media (DMEM supplemented with 10\% heat-inactivated fetal bovine serum, 2 mM L-glutamine, 100 U of penicillin/ml, and 100 \si{\micro}g of streptomycin/ml) at 37 \si{\degreeCelsius} at 5 \% CO\textsubscript{2}.

@@

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell}~\citep[][copy archived at \url{https://github.com/elifesciences-publications/flu_single_cell}]{russell2018github}.
